Baseline centering problem

### 2019-01-12 paper/icml_drau/dauc.tex
Algorithm description.

%! TEX root = icml_drau.tex
\begin{algorithmic}
	\STATE \textbf{Inputs:}
	\STATE $\theta_1$ and $\theta_2$, parameters of
	$V_{\theta_1}$ and $\bar{A}_{\theta_2}$.
	\STATE $\theta_1'$ parameter of target $V_{\theta_1'}$.
	\STATE $\pi_{\text{exp}}$ exploration policy.
	\STATE \textbf{opt}$_1$, \textbf{opt}$_2$, $\eta_1$ and $\eta_2$ optimizers and learning rates.
	\STATE $\mathcal{D}$, buffer of transitions $(s, a, r, d, s')$.
	\STATE $\deltat$ and $\gamma$, time discretization and discount factor.
	\STATE $\tau$, target network update factor.
	\STATE \textbf{nb\_epochs} number of epochs.
	\STATE \textbf{nb\_steps}, number of steps per epoch.
	\STATE
	\STATE Observe initial state $s^0$
	\STATE $t \gets 0$
	\FOR {$e=0, \textbf{nb\_epochs}$}
	\FOR {$k=1, \textbf{nb\_steps}$}
	\STATE Sample $a_t$ according to $\pi_{\text{exp}}$.
	\STATE Perform $a_t$ and observe $(r_{t+1}, d_{t+1}, s_{t+1})$.
	\STATE Store $(s_t, a_t, r_{t+1}, d_{t+1}, s_{t+1})$ in $\mathcal{D}$.
	\STATE Update $\pi_{\text{exp}}$ with $(a_t, s_{t+1})$.
	\STATE $t \gets t + 1$
	\ENDFOR
	\FOR {$k=0, \text{nb\_learn}$}
	\STATE \text{Sample a batch of $N$ random transitions from $\mathcal{D}$}
	\STATE $Q^i \gets V_{\theta_1}(s^i) + \deltat\hspace{-.17em}\left(
	\bar{A}_{\theta_2}(s^i, a^i) - \max\limits_{a'}\bar{A}_{\theta_2}(s^i, a')\right)$
	\STATE $\tilde{Q^i} \gets r^i + (1 - d^i) \gamma^{\deltat} V_{\theta_1}(s'^i)$
	\STATE $\Delta \theta_1 \gets \sum\limits_{i=1}^N \partial_{\theta_1} V_{\theta_1}(s^i) (Q^i - \tilde{Q^i})$
	\STATE $\Delta \theta_2 \gets \sum\limits_{i=1}^N \partial_{\theta_2} A_{\theta_2}(s^i, a^i) (Q^i - \tilde{Q^i})$
	\STATE Update $\theta_1$ using \textbf{opt}$_1$ with $\Delta \theta_1$ and learning rate $\eta_1$.
	\STATE Update $\theta_2$ using \textbf{opt}$_2$ with $\Delta \theta_2$ and learning rate $\eta_2$.
	\STATE $\theta_1' \gets \tau \theta_1' + (1 - \tau) \theta_1$
	\ENDFOR
	\ENDFOR
\end{algorithmic}

>>>>

%! TEX root = icml_drau.tex
\begin{algorithmic}
	\STATE \textbf{Inputs:}
	\STATE $\theta$ and $\psi$, parameters of
	$V_{\theta}$ and $\bar{A}_{\psi}$.
	\STATE $\pi^{\text{explore}}$ and $\nu_\deltat$ defining an exploration policy.
	\STATE \textbf{opt}$_1$, \textbf{opt}$_2$, $\alpha_1 \deltat$ and $\alpha_2 \deltat$ optimizers and learning rates.
	\STATE $\mathcal{D}$, buffer of transitions $(s, a, r, d, s')$, with $d$ the episode termination signal.
	\STATE $\deltat$ and $\gamma$, time discretization and discount factor.
	\STATE \textbf{nb\_epochs} number of epochs.
	\STATE \textbf{nb\_steps}, number of steps per epoch.
	\STATE
	\STATE Observe initial state $s^0$
	\STATE $t \gets 0$
	\FOR {$e=0, \textbf{nb\_epochs}$}
	\FOR {$j=1, \textbf{nb\_steps}$}
	\STATE $a^k \leftarrow \pi^{\text{explore}}(s^k, \nu^k_\deltat)$.
	\STATE Perform $a^k$ and observe $(r^{k+1}, d^{k+1}, s^{k+1})$.
	\STATE Store $(s^k, a^k, r^{k+1}, d^{k+1}, s^{k+1})$ in $\mathcal{D}$.
	\STATE $k \gets k + 1$
	\ENDFOR
	\FOR {$k=0, \text{nb\_learn}$}
	\STATE \text{Sample a batch of $N$ random transitions from $\mathcal{D}$}
	\STATE $Q^i \gets V_{\theta}(s^i) + \deltat\hspace{-.17em}\left(
	\bar{A}_{\psi}(s^i, a^i) - \max\limits_{a'}\bar{A}_{\psi}(s^i, a')\right)$
	\STATE $\tilde{Q^i} \gets r^i\deltat + (1 - d^i) \gamma^{\deltat} V_{\theta}(s'^i)$
	\STATE $\Delta \theta \gets \frac{1}{N}\sum\limits_{i=1}^N  \frac{\left(Q^i - \tilde{Q^i}\right)\partial_{\theta} V_{\theta}(s^i)}{\deltat}$
	\STATE $\Delta \psi \gets \frac{1}{N}\sum\limits_{i=1}^N \frac{\left(Q^i - \tilde{Q^i}\right)\partial_{\psi} \left(\bar{A}_{\psi}(s^i, a^i) - \max\limits_{a'}\bar{A}_{\psi}(s^i, a')\right) }{\deltat}$
	\STATE Update $\theta$ with \textbf{opt}$_1$, $\Delta \theta$ and learning rate $\alpha_1 \deltat$.
	\STATE Update $\psi$ with \textbf{opt}$_2$, $\Delta \psi$ and learning rate $\alpha_2 \deltat$.
	\ENDFOR
	\ENDFOR
\end{algorithmic}

### 2019-01-12 paper/tangotd.tex

Building a universal policy. One may make the policy depend on a goal
representation $\omega$ as an additional input. One may simultaneously
compute $Z(s_1,s_2,\omega)$, namely the $Z$ function when following the
policy with goal $\omega$, and train at the same time a map $s_2\mapsto \omega=\Omega(s_2)$ and
policy parameters $\pi(a|s_1,\omega)$ such that following
$\pi(|\Omega(s_2))$ indeed goes towards $s_2$, namely, the policy
gradient for every $s_2$ is
\begin{equation}
\partial \pi(a|s,\Omega(s_2))\E_{s'|s,a} \E_{s_2\sim \rho} \,
(z(s',s_2,\Omega(s_2))-z(s,s_2,\Omega(s_2)))
\end{equation}
[TODO check this is indeed the policy gradient for the time spent at
$s_2$ if following policy $\pi(|\Omega(s_2))$]. Advantage: diversity of
policies should appear by itself, no need to manually force options to be
distinct. Depends on a chosen distribution of goals $s_2$. TODO check:
this is with a reward a Dirac at $s_2$, check there's no technical
problem wrt the reference distribution $\rho(s_2)$, as we use $z$ not $Z$
in the policy gradient and $z$ is the density of $Z$ wrt $\rho$ but I
think it's correct. Actually, for goal representations, a goal is not
necessarily a state itself, should be a feature of states, or some
representation of a reward function, so we should figure out the way to
give a meaning to $\Omega(R)$ for an arbitrary reward $R$. The
representation of $Z$ as $Z=\transp{\green}f$ does that automatically,
thanks to linearity wrt $R$.

>>>>

Building a universal policy. One may make the policy depend on a goal
representation $\omega$ as an additional input. One may simultaneously
compute $Z(s_1,s_2,\omega)$, namely the $Z$ function when following the
policy with goal $\omega$, and train at the same time a map $s_2\mapsto \omega=\Omega(s_2)$ and
policy parameters $\pi(a|s_1,\omega)$ such that following
$\pi(|\Omega(s_2))$ indeed goes towards $s_2$, namely, the policy
gradient for every $s_2$ is
\begin{equation}
\partial \pi(a|s,\Omega(s_2))\E_{s'|s,a} \E_{s_2\sim \rho} \,
(z(s',s_2,\Omega(s_2))-z(s,s_2,\Omega(s_2)))
\end{equation}
[TODO check this is indeed the policy gradient for the time spent at
$s_2$ if following policy $\pi(|\Omega(s_2))$]. Advantage: diversity of
policies should appear by itself, no need to manually force options to be
distinct. Depends on a chosen distribution of goals $s_2$; we could learn
to go to uniformly distributed states, or create a goal at points where
we observe a high reward value (so learning to go to all states with a
reward). Just fixing $\Omega(s)\deq s$ once and for all might work, in
principle, but may be ambitious. TODO check:
this is with a reward a Dirac at $s_2$, check there's no technical
problem wrt the reference distribution $\rho(s_2)$, as we use $z$ not $Z$
in the policy gradient and $z$ is the density of $Z$ wrt $\rho$ but I
think it's correct. Actually, for goal representations, a goal is not
necessarily a state itself, should be a feature of states, or some
representation of a reward function, so we should figure out the way to
give a meaning to $\Omega(R)$ for an arbitrary reward $R$. The
representation of $Z$ as $Z=\transp{\green}f$ does that automatically,
thanks to linearity wrt $R$.
